---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rotor

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/s-fleck/rotor.svg?branch=master)](https://travis-ci.org/s-fleck/rotor)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Codecov test coverage](https://codecov.io/gh/s-fleck/rotor/branch/master/graph/badge.svg)](https://codecov.io/gh/s-fleck/rotor?branch=master)
<!-- badges: end -->

**rotor** provides a cross platform R reimagination of
[logrotate](https://linux.die.net/man/8/logrotate). It is a companion package to
the logging package [lgr](https://github.com/s-fleck/lgr). In addition to
rotating log files, it can also be used as a (primitive) backup tool. For
conditionally creating and deleting backups, rotor relies solely on information
encoded in a suffix of the backup file names (i.e. a timestamp or index). It
therefore also works with backups created by other tools, as long as the
filename has a format that rotor can understand.

`rotate()`, `rotate_date()`, and `rotate_time()` move a file and insert a suffix
(either an integer or a timestamp) into the filename. In addition, they create
an empty file in place of the original one. This is useful for log rotation.
`backup()`, `backup_date()` and `backup_time()` do the same but keep the
original file.

See the 
[function reference](https://s-fleck.github.io/rotor/reference/index.html) for 
more details

## Installation

You can install the released version of rotor from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rotor")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("s-fleck/rotor")
```
## Example

First we create a temporary directory for the files created by the code examples
```{r setup, results = "hide"}
library(rotor)

# create a directory
td <- file.path(tempdir(), "rotor")
dir.create(td, recursive = TRUE)

# create an example logfile
tf <- file.path(td, "mylogfile.log")
writeLines("An important message", tf)
```

`backup()` makes a copy of a file and inserts an index between the filename
and the file extension. The file with the index `1` is always the most recently
made backup.
```{r backup index, collapse=TRUE}
backup(tf)

# backup and rotate also support compression
backup(tf, compression = TRUE) 

# display backups of a file
list_backups(tf)  
```

`rotate()` also backs up a file, but replaces the original file with an empty 
one.

```{r rotate index, collapse=TRUE}
rotate(tf)
list_backups(tf)

# the original file is now empty
readLines(tf)

# its content was moved to the first backup
readLines(list_backups(tf)[[1]])

# we can now safely write to the original file
writeLines("another important message", tf)
```

The `max_backups` parameter limits the maximum number of backups rotor will
keep of a file. Notice how the zipped backup we created above moves to index 4 
as we create two new backups.
```{r}
backup(tf, max_backups = 4)
backup(tf, max_backups = 4)

list_backups(tf)
```

We can also use `prune_backups()` to delete old backups. Other than ensuring
that no new backups is created, it works identically to using `backup()` with
the `max_backups` parameter. By setting it to `0`, we delete all backups.
```{r}
prune_backups(tf, max_backups = 0)
```

Besides creating backup up with an index, **rotor** can also create timestamped 
backups. 
```{r timestamp}
backup_date(tf)
rotate_time(tf)
list_backups(tf)
```
```{r}
prune_backups(tf, max_backups = 0)  # cleanup
list_backups(tf)
```

Besides passing a total number of backups to keep, `max_backups` can also be 
a period or a date / datetime for timestamped backups.
```{r eval = FALSE}
# keep all backups younger than one year
prune_backups(tf, "1 year") 
  
# keep all backups from April 4th, 2018 and onwards
prune_backups(tf, "2018-04-01")  
```

```{r cleanup, include = FALSE}
unlink(td, recursive = TRUE)
```


# Dependencies

**rotor**'s dependencies are intentionally kept slim. It only comes with two
non-base dependencies:

* [R6](https://github.com/r-lib/R6): A light weight system for 
  encapsulated object-oriented programming.
* [dint](https://github.com/s-fleck/dint): A toolkit for working year-quarter 
  and year-month dates that I am also the author of. It is used by 
  `rotate_date()` and `rotate_time()` to deal with calendar periods. 
  
Both packages have no transitive dependencies (i.e they do not depend on 
anything outside of base R)
