---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rotor

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/s-fleck/rotor.svg?branch=master)](https://travis-ci.org/s-fleck/rotor)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

rotor is aimed to provide a cross platform R reimagination of
[logrotate](https://linux.die.net/man/8/logrotate) as a companion package to
https://github.com/s-fleck/lgr. In addition to rotating log files, it can also
be used as a (very primtivie) backup tool.

`rotate()`, `rotate_date()`, and `rotate_time()` move a file and insert a 
suffix (either an integer or a timestamp) into the filename. In addition, they
create an empty file in place of the original one. This is useful for log 
rotation.

`backup()`, `backup_date()` and `backup_time()` do the same but keep the 
original file. 

See the 
[function reference](https://s-fleck.github.io/rotor/reference/index.html) for 
more details

## Installation

<!-- You can install the released version of rotor from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rotor") -->
<!-- ``` -->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("s-fleck/rotor")
```
## Example

The examples below all use `backup()` because it's a bit more convenient to 
write examples for than `rotate()`, but the later works mostly the 
same.


```{r}
library(rotor)
```

First we must create a temporary directory and an example log file.
```{r setup, results = "hide"}
# setup test file for examples
dr <- tempdir()
td <- file.path(dr, "rotor")
dir.create(td, recursive = TRUE)
tf <- file.path(td, "test.log")
saveRDS(cars, tf)
```


`backup()` makes a copy of a file and inserts an index between the filename
and the file extension. The file with the index `1` is always the most recently
made backup.
```{r index, collapse=TRUE}
backup(tf)
backup(tf)
backup(tf, compression = TRUE)  # backup and rotate also support compression

list_backups(tf)  # returns all backups of a file
```

You can also set a maximum number of backups to be kept
```{r}
backup(tf, max_backups = 4)
backup(tf, max_backups = 4)
backup(tf, max_backups = 4)

list_backups(tf)
```

`prune_backups()` deletes all backups of a file except for `max_backups`. If
we set `max_backups` to `0`, we can clean up all backups.
```{r}
prune_backups(tf, max_backups = 0)
```



Instead of backup up with an index, you can also add a timestamp. 
```{r timestamp}
backup_date(tf)
backup_time(tf)
list_backups(tf)
```
```{r}
prune_backups(tf, max_backups = 0)  # cleanup
list_backups(tf)
```

```{r cleanup, include = FALSE}
unlink(td, recursive = TRUE)
if (!length(list.files(dr))) unlink(dr, recursive = TRUE)
```
