---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rotor

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/s-fleck/rotor.svg?branch=master)](https://travis-ci.org/s-fleck/rotor)
<!-- badges: end -->

rotor is aimed to provide a cross platform R reimagination of
[logrotate](https://linux.die.net/man/8/logrotate) as a companion package to
https://github.com/s-fleck/lgr. 

## Installation

<!-- You can install the released version of rotor from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rotor") -->
<!-- ``` -->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("s-fleck/rotor")
```
## Example

`rotate()` and `rotate_date()` rename a file and insert a suffix (either an
integer or a timestamp) into the filename. This is useful for log rotation.

`backup()` and `backup_date()` do the same but keep the original file,
thus creting a backup. The examples below use `backup*()` because it's a bit
more convenient to write examples for, but `rotate()` works mostly the same.


```{r setup, results = "hide"}
library(rotor)

# setup test file for examples
td <- file.path(tempdir(), "rotor")
dir.create(td, recursive = TRUE)
tf <- file.path(td, "test.log")
file.create(tf)
```
```{r}
cat(tf)
```

`backup()` makes a copy of a file and inserts an index between the filename
and the file extension. The file with the index `1` is always the most recently
made backup.
```{r index, collapse=TRUE}
backup(tf)
backup(tf)
backup(tf, compression = "zip")  # backup and rotate also support compression

find_backups(tf)  # returns all backups of a file
```

You can also set a maximum number of backups to be kept
```{r}
backup(tf, max_backups = 4)
backup(tf, max_backups = 4)
backup(tf, max_backups = 4)

find_backups(tf)
```

```{r}
invisible(file.remove(find_backups(tf)))  # cleanup
```



Instead of adding an index, you can also add a timestamp. The format of the
timestamp can be arbitrary (see `?format.POSIXct`), but it must be lexically 
sortable so that `max_backups` does the right thing; i.e. `2019-02-18` is good, 
but `18-02-2019` is not.

```{r timestamp}
backup_date(tf)
find_backups(tf)
```
```{r}
invisible(file.remove(find_backups(tf)))  # cleanup
```


